\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx}

\title{Analysis of Lock-Free Scalable Vector Performance in High-Concurrency Environments}
\author{ByeongKyu Park}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}
This document presents an analysis of a Lock-Free Sorted Vector (LFSV) designed for high-concurrency environments. Unlike traditional approaches that may rely on lock-based synchronization mechanisms, the LFSV leverages atomic operations to ensure thread safety and high performance. A key aspect of our implementation is the **Garbage Remover** component, which provides an efficient memory management strategy by deferring the deletion of vector elements.

\section{Implementation}
The LFSV is implemented with a focus on the Garbage Remover component for efficient memory management in a concurrent setting:
\begin{itemize}
    \item \textbf{Garbage Remover:} Safely deletes vectors after a delay, preventing use-after-free errors and reducing dynamic allocation overhead, thus minimizing lock contention.
\end{itemize}
This approach allows for safe updates and access by multiple threads without serializing access, leveraging atomic operations for consistency.

\section{Performance Evaluation}
Performance was evaluated under different thread counts, with the following updated results observed:

\begin{table}[h]
\centering
\begin{tabular}{|l|l|l|}
\hline
\textbf{Number of Threads} & \textbf{Operations per Thread} & \textbf{Execution Time (seconds)} \\ \hline
1                          & 21000                          & 0.498376                          \\ \hline
2                          & 10500                          & 0.439024                          \\ \hline
3                          & 7000                           & 0.44203                           \\ \hline
4                          & 5250                           & 0.391371                          \\ \hline
5                          & 4200                           & 0.379913                          \\ \hline
8                          & 2625                           & 0.290448                          \\ \hline
16                         & 1313                           & 0.333443                          \\ \hline
\end{tabular}
\caption{Updated LFSV Performance Results}
\label{table:updated_performance}
\end{table}

\section{Analysis}
The updated results indicate a trend of improved performance with an increase in threads, up to a certain point. This highlights the efficiency of the LFSV's lock-free design and the effectiveness of the Garbage Remover in managing concurrent operations. 

\section{Conclusion}
The LFSV, with its innovative use of the Garbage Remover for memory management, demonstrates significant potential for enhancing performance in concurrent applications. This lock-free data structure improves scalability and efficiency, making it an excellent choice for modern software development in high-concurrency environments. Future work will explore further optimizations and the impact of various hardware configurations on performance.

\end{document}
